### 2014-03-25 trunk/paper_enahpc14/draft.tex
updates bibliography and introduction

%%%%%%%%%%%%%%%%%%%%%%% file draft.tex %%%%%%%%%%%%%%%%%%%%%%%%%
%
% This is a general template file for the LaTeX package SVJour3
% for Springer journals.          Springer Heidelberg 2010/09/16
%
% Copy it to a new file with a new name and use it as the basis
% for your article. Delete % signs as needed.
%
% This template includes a few options for different layouts and
% content for various journals. Please consult a previous issue of
% your journal as needed.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% First comes an example EPS file -- just ignore it and proceed on the
% \documentclass line your LaTeX will extract the file if required
\begin{filecontents*}{example.eps}
%!PS-Adobe-3.0 EPSF-3.0
%%BoundingBox: 19 19 221 221
%%CreationDate: Mon Sep 29 1997
%%Creator: programmed by hand (JK)
%%EndComments
gsave
newpath
  20 20 moveto
  20 220 lineto
  220 220 lineto
  220 20 lineto
closepath
2 setlinewidth
gsave
  .4 setgray fill
grestore
stroke
grestore
\end{filecontents*}
%
\RequirePackage{fix-cm}
%
%\documentclass{svjour3}                     % onecolumn (standard format)
%\documentclass[smallcondensed]{svjour3}     % onecolumn (ditto)
%\documentclass[smallextended]{svjour3}      % onecolumn (second format)
\documentclass[twocolumn]{svjour3}           % twocolumn
%
\smartqed % flush right qed marks, e.g. at end of proof
%
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage[round, sort, numbers, authoryear]{natbib}
%
% please place your own definitions here and don't use \def but
% \newcommand{}{}
%
% Insert the name of "your journal" with
% \journalname{myjournal}
%
\begin{document}

@@

\author{J.Charles \and M.Dolz}

@@

\institute{Dr. Joseph Charles \at Swiss National Supercomputing Centre
  (CSCS)\\ CH-6900  Lugano, Switzerland \\  Tel.: +41 (0) 91  610 8216
  \\  \email{joseph.charles@cscs.ch}  \\  \and  Dr.  Manuel  Dolz  \at
  University of Hamburg \\ 20148  Hamburg, Germany \\ Tel.: +49 (0) 40
  460094-404 \\ \email{manuel.dolz@informatik.uni-hamburg.de}}

@@

\begin{abstract}
  In this paper we present  COSMO-ART, an extension of the operational
  weather  forecast  model  of   the  German  Weather  Service  (DWD),
  developed for  the evaluation of the interactions  of reactive gases
  and aerosol particles  with the state of atmosphere  at the regional
  scale. It  includes secondary aerosols,  directly emitted components
  like  soot,  mineral  dust,  sea  salt and  biological  material  as
  pollen. Processes such  as emissions, coagulation, condensation, dry
  deposition,  wet removal,  and sedimentation  of aerosols  are taken
  into account.   The overall performance  of this application  on HPC
  systems is  analysed by a  profiling and tracing study  to determine
  hotspots, i.e.  the  parts of the program that  require the dominant
  fraction of runtime, and to identify critical paths, i.e.  sequences
  of functions that shows dominant inclusive contributions for all its
  elements. Moreover, we describe measurement devices and energy-aware
  techniques  employed  to  evaluate   the  energy  footprint  of  the
  considered  application and  to  get detailed  insights about  power
  bottlenecks.  Our approach is to improve corresponding code sections
  to  sustain high  performance  while minimizing  energy-to-solution.
  This preliminary  study sets the basis of  broader considerations to
  tackle challenges  related to energy efficient HPC  in the framework
  of the Exa2Green project (\url{http://exa2green.eu/}).

\keywords{High performance computing  \and Energy-aware computing \and
  Numerical Weather Prediction}
% \PACS{PACS code1 \and PACS code2 \and more}
% \subclass{MSC code1 \and MSC code2 \and more}
\end{abstract}

@@

\begin{acknowledgements}
The  authors  would  like  to  thank the  High  Performance  and  High
Productivity  Computing  (\url{www.hp2c.ch})  Initiative and  the  FP7
funding this project.)
\end{acknowledgements}

%\bibliographystyle{spbasic}  % basic style, author-year citations
%\bibliographystyle{spphys}   % APS-like style for physics
%\bibliographystyle{spmpsci}  % mathematics and physical sciences
\bibliographystyle{unsrtnat}

\bibliography{draft}  % name your BibTeX data base

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% This is a general template file for the LaTeX package SVJour3
% for Springer journals.          Springer Heidelberg 2010/09/16
%
% Copy it to a new file with a new name and use it as the basis
% for your article. Delete % signs as needed.
%
% This template includes a few options for different layouts and
% content for various journals. Please consult a previous issue of
% your journal as needed.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% First comes an example EPS file -- just ignore it and proceed on the
% \documentclass line your LaTeX will extract the file if required
\begin{filecontents*}{example.eps}
%!PS-Adobe-3.0 EPSF-3.0
%%BoundingBox: 19 19 221 221
%%CreationDate: Mon Sep 29 1997
%%Creator: programmed by hand (JK)
%%EndComments
gsave
newpath
  20 20 moveto
  20 220 lineto
  220 220 lineto
  220 20 lineto
closepath
2 setlinewidth
gsave
  .4 setgray fill
grestore
stroke
grestore
\end{filecontents*}
%
\RequirePackage{fix-cm}
%
%\documentclass{svjour3}                     % onecolumn (standard format)
%\documentclass[smallcondensed]{svjour3}     % onecolumn (ditto)
%\documentclass[smallextended]{svjour3}      % onecolumn (second format)
\documentclass[twocolumn]{svjour3}           % twocolumn
%
\smartqed % flush right qed marks, e.g. at end of proof
%
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage[round, sort, numbers, authoryear]{natbib}
%
\DeclareRobustCommand\IPCClongname{}
%
% please place your own definitions here and don't use \def but
% \newcommand{}{}
%
% Insert the name of "your journal" with
% \journalname{myjournal}
%
\begin{document}

@@

\author{J.Charles \and W.Sawyer \and M.Dolz \and C.Malossi}

@@

\institute{Dr. Joseph Charles \at Swiss National Supercomputing Centre
  (CSCS)\\ CH-6900  Lugano, Switzerland  \\ Tel: +41  (0) 91  610 8216
  \\ \email{joseph.charles@cscs.ch} \and Dr.  William Sawyer \at Swiss
  National Supercomputing Centre  (CSCS)\\ CH-6900 Lugano, Switzerland
  \\ Tel:  +41 (0) 91 610 8229  \\ \email{william.sawyer@cscs.ch} \and
  Dr.  Manuel Dolz \at University of Hamburg \\ 20148 Hamburg, Germany
  \\         Tel:         +49         (0)        40         460094-404
  \\ \email{manuel.dolz@informatik.uni-hamburg.de}  \and Dr. Cristiano
  Malossi  \at  IBM  Zurich  Research Laboratory  \\  CH-8000  Zurich,
  Switzerland     \\     Tel:      +41     (0)     44     724     8616
  \\ \email{ACM@zurich.ibm.com}}

@@

\begin{abstract}
  In this paper we present  COSMO-ART, an extension of the operational
  weather  forecast  model  of   the  German  Weather  Service  (DWD),
  developed for  the evaluation of the interactions  of reactive gases
  and aerosol particles  with the state of atmosphere  at the regional
  scale. It  includes secondary aerosols,  directly emitted components
  like  soot,  mineral  dust,  sea  salt and  biological  material  as
  pollen. Processes such  as emissions, coagulation, condensation, dry
  deposition,  wet removal,  and sedimentation  of aerosols  are taken
  into account.   The overall performance  of this application  on HPC
  systems is  analysed by a  profiling and tracing study  to determine
  hotspots, i.e.  the  parts of the program that  require the dominant
  fraction of runtime, and to identify critical paths, i.e.  sequences
  of functions that shows dominant inclusive contributions for all its
  elements. Moreover, we describe measurement devices and energy-aware
  techniques  employed  to  evaluate   the  energy  footprint  of  the
  considered  application and  to  get detailed  insights about  power
  bottlenecks.   Our  motivation  is  to  improve  corresponding  code
  sections    to   sustain    high   performance    while   minimizing
  energy-to-solution.   This  preliminary  study  sets  the  basis  of
  broader  considerations  to  tackle  challenges  related  to  energy
  efficient   HPC  in   the   framework  of   the  Exa2Green   project
  (\url{http://exa2green.eu/}).

\keywords{High performance computing  \and Energy-aware computing \and
  Green computing  \and Numerical Weather  Prediction \and Atmospheric
  Chemistry \and Aerosol Modelling \and COSMO-ART}
% \PACS{PACS code1 \and PACS code2 \and more}
% \subclass{MSC code1 \and MSC code2 \and more}
\end{abstract}

@@

\begin{acknowledgements}
This  research  was  supported   by  the  Exa2Green  research  project
co-funded  under the  EU  7th Framework  Program  Future and  Emerging
Technologies (FET) Proactive Initiative: Minimising Energy Consumption
of Computing to  the Limit (MINECC).  The authors  would like to thank
the    High    Performance    and    High    Productivity    Computing
(\url{www.hp2c.ch}) Initiative.)
\end{acknowledgements}

\DeclareRobustCommand\IPCClongname{ Intergovernmental Panel on Climate Change}
\bibliographystyle{plainnat}
\bibliography{\jobname}
